An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-06-06 poly-embed-journal/poly-embed-journal.tex
Pass over Prop 7 with equivalence class definition of trim

%\jessie{In general, we shall denote discrete reports by $r \in \R$, and real-valued reports by $u \in \U$.}
For example, 0-1 loss is a discrete loss with $\R = \Y = \{-1,1\}$
given by $\ellzo(r)_y = \Ind{r \neq y}$, with Bayes risk $\risk{\ellzo}(p) = 1-\max_{y\in\Y} p_y$.
Two important surrogates for $\ellzo$ are hinge loss $\hinge(u)_y = (1-yu)_+$, where $(x)_+ = \max(x,0)$, and logistic loss $L(u)_y = \log(1+\exp(-yu))$ for $u\in\reals$.
See Figures~\ref{fig:0-1-br},~\ref{fig:hinge-br}, and~\ref{fig:logistic-br} for a visualization of the Bayes risks of 0-1, Hinge, and Logistic losses, respectively.

@@

Appendix~\ref{app:calibration} contains the full proof; this section provides a sketch along with the main construction and result.
The first step is to give a link $\psi$ such that exactly minimizing expected surrogate loss $L$, followed by applying $\psi$, always exactly minimizes expected original loss $\ell$.
The existence of such a link is somewhat subtle, because in general some point $u$ that is far from any embedding point can minimize expected loss for two very different distributions $p,p'$, making it unclear whether there exists a choice $\psi(u)\in\R$ that is $\ell$-optimal for both distributions.
We show that as we vary $p$ over $\simplex$, there are only finitely many sets of the form $U = \argmin_{u \in \reals^d} \inprod{p}{L(u)}$ (Lemma~\ref{lem:polyhedral-range-gamma}).
Associating each $U$ with $R_U \subseteq \R$, the set of reports whose embedding points are in $U$, we enforce that all points in $U$ link to some report in $R_U$.
(As a special case, embedding points must link to their corresponding reports.)
Proving that these choices are well-defined uses a chain of arguments involving the Bayes risk, ultimately showing that if $u$ lies in multiple such sets $U$, the corresponding report sets $R_U$ all intersect at some $r =: \psi(u)$.

@@

\begin{restatable}{proposition}{embedtrim}\label{prop:embed-trim}
  Let $\Gamma:\simplex\toto\reals^d$ be an elicitable property.
  The following are equivalent:
  \begin{enumerate}\setlength{\itemsep}{0pt}
  \item $\Gamma$ embeds a elicitable finite property $\gamma:\simplex \toto \R$.
  \item $\trimnonred(\Gamma)$ is a finite set, and $\cup\,\trimnonred(\Gamma) = \simplex$.
  % \\ $\hat\Gamma := \trimnonred(\Gamma)$ is a finite property, and $\cup\,\hat\Gamma) = \simplex$.
  \item There is a finite minimum representative set $\U$ for $\Gamma$.
  \item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$, and $\cup\,\Theta = \simplex$.
  \end{enumerate}
  % \raft{I see why you wanted this addition here, but (a) it's clear from the def of embedding, and (b) we don't have varphi defined.  So let's leave it out.}
  Moreover, when any of the above hold, $\trimnonred(\gamma) = \trimnonred(\Gamma) = \{\Gamma_u : u\in\U\} = \Theta$.\jessiet{Also, should this statement be $\trimcover(\gamma) = \trimnonred(\gamma) = \trimcover(\Gamma) = \trimnonred(\Gamma) = \{\Gamma_u \mid u \in \U\} = \Theta$? But also, can we pull it out into its own statement? It should follow as a corollary of this and an analogous version of Prop 6.}
\end{restatable}
\begin{proof}
	\jessie{Keep plus example in mind}
	\jessie{Use trim nonredundant and trim covering macros}
	\jessie{1 -> 2 -> 3 -> 1, 3 <=> 4}
	Let $L$ elicit $\Gamma$.

	1 $\Rightarrow$ 2:
	%
	% \jessie{Loss intuition: Let $L$ elicit $\Gamma$.  If $\Gamma$ embeds a finite $\gamma'$, $L$ must embed a discrete loss $\ell$ such that $\ell(r) = L(\varphi(r))$.  Therefore, $\risk{L} = \risk{\ell}$ is polyhedral. Moreover, we have $\Gamma$ also embedding the finite property $\prop{\ell} := \gamma$ as a corollary of the definition of embedding properties. We claim $\trim(\Gamma) = \{\gamma_r : r \in \R\}$ (Lemma~\ref{lem:embedded-level-sets-trim}), and since the latter set is finitely generated (as $\R$ is finite), we have have $\trim(\Gamma)$ is finite.  Moreover, as $\gamma$ is nondegenerate (since it is defined over the simplex), we have that $\cup_{r \in \R} \gamma_r = \simplex$.}
	%
%	Since $\gamma$ is finite, it has a finite minimum representative set $\Sc$, and we can show $\trimnonred(\gamma) = \trimcover(\gamma) := \{\gamma_r \mid r \in \Sc\}$. 
%	\jessiet{Hand waving}
%	Moreover, since the embedding condition implies $\gamma_r = \Gamma_{\varphi(r)}$, we also have $\trimcover(\Gamma) = \trimcover(\gamma)$, which is finite as $\gamma$ is finite.
%	Now we can show that $\trimcover(\Gamma)$ finite implies $\trimcover(\Gamma) = \trimnonred(\Gamma)$ and the result follows.
%
	%Since $\Gamma$ embeds a finite $\gamma$ over some minimum representative set $\Sc$, and each for each $r \in \Sc$, we have $\gamma_r = \Gamma_{\varphi(r)}$.
	%
	Since $\R$ is finite, we have $\trimnonred(\Gamma) \subseteq \{\Gamma_{\varphi(r)} \mid r \in \R\} = \{\gamma_r \mid r \in \R\}$.
	As the last set is finite, so is $\trimnonred(\Gamma)$.
	Moreover, as $\trimnonred$ only removes redundant reports, we have $\cup \trimnonred(\Gamma) = \simplex$.

@@

	2 $\Rightarrow$ 3: 
	%Suppose $\trimcover(\Gamma) = \{\Gamma_u \mid u \in \U\}$.
	%Then we know $\U$ is a minimum representative set, and since $\trimcover(\Gamma)$ is finite, so is $\U$; if it was not, then $\U$ would not be minimum.
	\jessie{Using the old definition of $\trim := \trimnonred$, mirroring ish previous proofs} 
	As a reminder, we have $\trimnonred(\Gamma) = \{\Gamma_u \mid \neg \exists u' \neq u $ s.t. $ \Gamma_u \subsetneq \Gamma_{u'}\}$.
	Take $\U^* = \{u_1, \ldots, u_k\}$ to be a finite set of reports forming $\trimnonred$.
	Since $\cup \trimnonred(\Gamma) = \cup_{u \in \U^*} \Gamma_u = \simplex$, we have $\U^*$ representative.
	We can now construct a minimum representative set $\U \subseteq \U^*$.
	Form $\U$ by iterating over $\U^*$ and removing any element $u'$ of $\U^*$ if there is another $u$ remaining in $\U^*$ such that $\Gamma_u = \Gamma_{u'}$.
	As we only remove exact duplicate level sets, we still have $\U$ representative, and proceed to show $\U$ is minimum.

	If $\U$ was not minimum, there would be some report $u' \in \U$ so that $\U' := \U \setminus \{u'\}$ is also representative.
	Since $\Gamma$ is elicitable and $\trimnonred$ is finite, we know that the level sets of $\Gamma$ form a power diagram intersected with the simplex (Theorem~\ref{thm:aurenhammer}).
	Therefore, every level set $\Gamma_u$ corresponds to a face of a convex polyhedron: we correspond in two cases, according to if $\Gamma_{u'}$ corresponds to a facet or some lower-dimensional face.

	First, suppose $\Gamma_{u'}$ does not correspond to a facet.
	Since $\Gamma_{u'}$ does correspond to a face of a convex polytope, it must be contained in a facet, and therefore there is some $u$ such that $\Gamma_{u'} \subsetneq \Gamma_u$.
	Thus, $\Gamma_u \not \in \trimnonred(\Gamma)$.
	If $\Gamma_{u'}$ corresponds to a facet, then it has a well-defined nonempty interior, and by removing exactly duplicate reports in the construction of $\U$, we have a $p \in \inter{\Gamma_{u'}}$ such that $\{u'\} = \Gamma(p)$.
	Therefore, $\U'$ would not be representative.
	We conclude $\U$ as constructed must be a minimum representative set.

	3 $\Rightarrow$ 1:
	Since $\U$ is representative, we have $\Gamma|_\U(p) := \Gamma(p) \cap \U$ nonempty for all $p \in \simplex$, and therefore, $\Gamma$ embeds $\Gamma|_\U$, which is finite as $\U$ is finite.
	Since $\U$ is minimum, the constructed $\Gamma_\U$ is additionally non-redundant.
	\jessiet{Want more details here.  It's the forward implication of Prop 4, but since this is used in the reverse implication of prop 4, don't want to create cyclic dependencies.}

@@

3 $\Rightarrow$ 4:
It suffices to show that, for each $u \in \U$, $\Gamma_u$ is full-dimensional, so we can take $\Theta = \{\Gamma_u \mid u \in \U\}$.
Since $\Gamma$ has a finite representative set, we know its level sets are faces of convex polyhedron by equivalence to a power diagram intersected with the simplex.
If there is a $u \in \U$ such that $\Gamma_u$ is not full-dimensional, it must be a face of some facet corresponding to $\Gamma_{u'}$ for some $u' \in \U$, and hence we contradict $\U$ being minimum, as $\U \setminus \{u\}$ would be a representative set of strictly smaller cardinality.

4 $\Rightarrow$ 3:
We want to show that for each $\theta \in \Theta$, we cannot have $\Theta' := \Theta \setminus \{\theta\}$ be representative.
Observe we have no duplicate elements of $\Theta$.
Fix $\theta := \Gamma_u \in \Theta$.
Since $\Gamma_u$ is full-dimensional, there is some $p \in \inter{\Gamma_u}$ so that $\{u\} = \Gamma(p)$.
Therefore, $\Theta'$ is not representative, so $\Theta$ is a finite minimum representative set for $\Gamma$.

Observe now that when one of these is true, $\Gamma|_\U$ is elicited by $L|_\U$, and that there is a bijection from $\Gamma|_\U$ to $\gamma$, and therefore $\gamma$ is also elicitable. 
\end{proof}

>>>>

%\jessie{In general, we shall denote discrete reports by $r \in \R$, and real-valued reports by $u \in \U$.}
For example, 0-1 loss is a discrete loss with $\R = \Y = \{-1,1\}$
given by $\ellzo(r)_y = \Ind{r \neq y}$, with Bayes risk $\risk{\ellzo}(p) = 1-\max_{y\in\Y} p_y$.
Two important surrogates for $\ellzo$ are hinge loss $\hinge(u)_y = (1-yu)_+$, where $(x)_+ = \max(x,0)$, and logistic loss $L(u)_y = \log(1+\exp(-yu))$ for $u\in\reals$.
See Figure~\ref{fig:bayes-risks-01} for a visualization of the Bayes risks of 0-1, Hinge, and Logistic losses, respectively.

@@

\S~\ref{app:calibration} contains the full proof; this section provides a sketch along with the main construction and result.
The first step is to give a link $\psi$ such that exactly minimizing expected surrogate loss $L$, followed by applying $\psi$, always exactly minimizes expected original loss $\ell$.
The existence of such a link is somewhat subtle, because in general some point $u$ that is far from any embedding point can minimize expected loss for two very different distributions $p,p'$, making it unclear whether there exists a choice $\psi(u)\in\R$ that is $\ell$-optimal for both distributions.
We show that as we vary $p$ over $\simplex$, there are only finitely many sets of the form $U = \argmin_{u \in \reals^d} \inprod{p}{L(u)}$ (Lemma~\ref{lem:polyhedral-range-gamma}).
Associating each $U$ with $R_U \subseteq \R$, the set of reports whose embedding points are in $U$, we enforce that all points in $U$ link to some report in $R_U$.
(As a special case, embedding points must link to their corresponding reports.)
Proving that these choices are well-defined uses a chain of arguments involving the Bayes risk, ultimately showing that if $u$ lies in multiple such sets $U$, the corresponding report sets $R_U$ all intersect at some $r =: \psi(u)$.

@@

\begin{restatable}{proposition}{embedtrim}\label{prop:embed-trim}
  Let $\Gamma:\simplex\toto\reals^d$ be an elicitable property.
  The following are equivalent:
  \begin{enumerate}\setlength{\itemsep}{0pt}
  \item $\Gamma$ embeds a elicitable finite property $\gamma:\simplex \toto \R$.
  \item $\trimnonred(\Gamma)$ is a finite set, and $\cup\,\trimnonred(\Gamma) = \simplex$.
  % \\ $\hat\Gamma := \trimnonred(\Gamma)$ is a finite property, and $\cup\,\hat\Gamma) = \simplex$.
  \item There is a finite minimum representative set $\U$ for $\Gamma$.
  \item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$, and $\cup\,\Theta = \simplex$.
  \end{enumerate}
  % \raft{I see why you wanted this addition here, but (a) it's clear from the def of embedding, and (b) we don't have varphi defined.  So let's leave it out.}
  Moreover, when any of the above hold, $\trimnonred(\gamma) = \trimnonred(\Gamma) = \{\Gamma_u \mid u\in\U\} = \Theta$.
\end{restatable}
\begin{proof}
	\jessie{Keep plus example in mind}
	\jessie{1 -> 2 -> 3 -> 1, 3 <=> 4}
	Let $L$ elicit $\Gamma$.

	1 $\Rightarrow$ 2:
	%
	% \jessie{Loss intuition: Let $L$ elicit $\Gamma$.  If $\Gamma$ embeds a finite $\gamma'$, $L$ must embed a discrete loss $\ell$ such that $\ell(r) = L(\varphi(r))$.  Therefore, $\risk{L} = \risk{\ell}$ is polyhedral. Moreover, we have $\Gamma$ also embedding the finite property $\prop{\ell} := \gamma$ as a corollary of the definition of embedding properties. We claim $\trim(\Gamma) = \{\gamma_r : r \in \R\}$ (Lemma~\ref{lem:embedded-level-sets-trim}), and since the latter set is finitely generated (as $\R$ is finite), we have have $\trim(\Gamma)$ is finite.  Moreover, as $\gamma$ is nondegenerate (since it is defined over the simplex), we have that $\cup_{r \in \R} \gamma_r = \simplex$.}
	%
%	Since $\gamma$ is finite, it has a finite minimum representative set $\Sc$, and we can show $\trimnonred(\gamma) = \trimcover(\gamma) := \{\gamma_r \mid r \in \Sc\}$. 
%	\jessiet{Hand waving}
%	Moreover, since the embedding condition implies $\gamma_r = \Gamma_{\varphi(r)}$, we also have $\trimcover(\Gamma) = \trimcover(\gamma)$, which is finite as $\gamma$ is finite.
%	Now we can show that $\trimcover(\Gamma)$ finite implies $\trimcover(\Gamma) = \trimnonred(\Gamma)$ and the result follows.
%
	%Since $\Gamma$ embeds a finite $\gamma$ over some minimum representative set $\Sc$, and each for each $r \in \Sc$, we have $\gamma_r = \Gamma_{\varphi(r)}$.
	%

	We show $\trimnonred(\gamma) = \trimnonred(\Gamma)$, and the result will follow, since $\gamma$ is a finite property, and therefore $\trim(\gamma)$ is also finite, but its level sets still union to the simplex since $\trimnonred(\cdot)$ only removes strictly redundant level sets.

	Suppose the finite loss $\ell$ elicits $\gamma$; the negative Bayes risk of $\ell$ is a convex polyhedral function, and the epigraph of negative risk $E_\ell$ is polyhedral.
	Each face of $E_\ell$ corresponds to a level set of $\gamma$ as the hyperplane $H^\ell_r : p \mapsto (p, \inprod{p}{-\ell(r)})$ supports $E_\ell$ on exactly the level set $\gamma_r$.
	Since the faces of $E_\ell$ are closed and convex polyhedron and $E_\ell$ is affinely equivalent to a power diagram (Theorem~\ref{thm:aurenhammer}), each each level set $\gamma_r$ is a face of a convex polyhedron.
	Moreover, each $\gamma_r \in \trimnonred(\gamma)$ is a facet, since any lower-dimensional face is contained in a facet.

	By embedding, we have $H^L_{\varphi(r)} = H^\ell_r$ for all $r \in \R$, and similarly, we have every $\Gamma_u$ is a region of support for the hyperplane $H^L_u$ and is therefore a face of $E_L$.

	Since $\Gamma$ embeds $\gamma$ and $\gamma$ is elicitable, we have $\gamma_r = \Gamma_{\varphi(r)}$ for all $r \in \Sc$ and therefore $E_L$ is also  polyhedral since $\varphi(\Sc)$ is representative.\jessiet{Do we need to worry about the technicality of embedding over $\Sc \subset \R$ or are we fine with elicitability of $\gamma$?}
	Observe that for any $s \in \R \setminus [\Sc]$\jessiet{$\{s' : s' \equiv s \in \Sc\}$}, $\gamma_{s} \not \in \trimnonred(\gamma)$ since $\Sc$ is representative\jessiet{hand waving}, which gives $\trimnonred(\Gamma) \supseteq \trimnonred(\gamma)$, and we just need to show the other direction of subset inclusion.

	Consider 2 cases: (a) $u \in \varphi(\R), u \in \U_\equiv$, (b) $u \not \in \varphi(\R), u \in \U_\equiv$.
	For (a), given $u = \varphi(r)$, we have $\gamma_r = \Gamma_u$ by the embedding condition, so $\Gamma_u$ also supports $E_L$ on a facet and is therefore not a strict subset of any other level set.
	Thus, $\Gamma_u \in \trimnonred(\gamma)$.
	(b) follows similarly, except that there has to be some $u'$ such that $u \equiv u'$ such that $u' = \varphi(r)$; we conclude $\gamma_r = \Gamma_{u'} = \Gamma_u$ by embedding then equivalence of reports.
	Therefore, $\Gamma_u \in \trimnonred(\gamma)$.
	%For (c), if $u \not \in \U_\equiv$, then we have $\Gamma_u \not \in \trimnonred(\Gamma)$, and the statement follows vacuously.
	We conclude $\trimnonred(\Gamma) = \trimnonred(\gamma)$, and (2) follows.

%	Suppose for contradiction that there was a $u \in \U_\equiv$ (e.g., $\Gamma_u \in \trimnonred(\Gamma)$) such that $\Gamma_u \neq \gamma_r$ for any $r \in \R_\equiv$.
%	We know that $\Gamma_u$ is not a subset of any other level set $\Gamma_{u'}$ for $u' \in \U_\equiv$.
%	However, for any $p \in \Gamma_u$, there is some $r \in \R_\equiv$ such that $p \in \gamma_r \cap \Gamma_{\varphi(r)}$ by properties being nonempty and the embedding condition.
%	Since we claim $u \not\equiv u'$,

@@

	2 $\Rightarrow$ 3: 
	%Suppose $\trimcover(\Gamma) = \{\Gamma_u \mid u \in \U\}$.
	%Then we know $\U$ is a minimum representative set, and since $\trimcover(\Gamma)$ is finite, so is $\U$; if it was not, then $\U$ would not be minimum.
	\jessie{Using the old definition of $\trim := \trimnonred$, mirroring ish previous proofs} 
	The result follows if we show $\U_\equiv$ is minimum.
	Recall $\trimnonred(\Gamma) = \{\Gamma_u \mid u \in \U_\equiv\}$.
	Since $\trimnonred(\Gamma)$ is finite and it is generated by $\U_\equiv$, so must $\U_\equiv$ by its construction containing no duplicate elements.
	Take any $\U = \{u \mid [u] \in \U_\equiv\}$ to be any finite set of reports forming $\trimnonred(\Gamma)$.
	Since $\cup \trimnonred(\Gamma) = \cup_{u \in \U} \Gamma_u = \simplex$, we have $\U$ representative, and just need to show $\U$ is minimum.

	If $\U$ was not minimum, there would be some report $u \in \U$ so that $\U \setminus \{u\}$ is also representative.
	Since $\Gamma$ is elicitable and $\trimnonred$ is finite, we know that the level sets of $\Gamma$ form a power diagram intersected with the simplex (Theorem~\ref{thm:aurenhammer}).
	Therefore, every level set $\Gamma_u$ is a face of a convex polyhedron: we correspond in two cases, according to if $\Gamma_{u}$ corresponds to a facet or some lower-dimensional face.
	If $\Gamma_{u}$ is not a facet (but must still be a face) of a convex polytope, it must be contained in a facet, and therefore there is some $u'$ such that $\Gamma_{u} \subsetneq \Gamma_{u'}$, so $\Gamma_u \not \in \trimnonred(\Gamma)$.
	If $\Gamma_{u}$ corresponds to a facet, then it has a well-defined nonempty interior, and since there is no $u' \in \U$ such that $u' \equiv u$ by construction of $\U$, we have a $p \in \inter{\Gamma_{u}}$ such that $\{u\} = \Gamma(p)$.
	Therefore, $\U \setminus \{u\}$ would not be representative.
	We conclude $\U$ as constructed must be a minimum representative set.

	3 $\Rightarrow$ 1:
	Since $\U$ is representative, we have $\gamma(p) := \Gamma(p) \cap \U$ nonempty for all $p \in \simplex$, and therefore, $\Gamma$ embeds $\Gamma|_\U$ via the identity, which is finite as $\U$ is finite.
	Since $\U$ is minimum, we additionally have $\{\gamma_u \mid u \in \U\} =  \{\Gamma_u \mid u \in \U\} =\trimnonred(\gamma)$ by construction both of $\gamma$ and of $\U$.

@@

3 $\Rightarrow$ 4:
It suffices to show that, for each $u \in \U$, $\Gamma_u$ is full-dimensional, so we can take $\Theta = \{\Gamma_u \mid u \in \U\}$.
Since $\Gamma$ has a finite representative set, we know its level sets are faces of convex polyhedron by equivalence to a power diagram intersected with the simplex (Theorem~\ref{thm:aurenhammer}).
If there is a $u \in \U$ such that $\Gamma_u$ is not full-dimensional, it must be a face of some facet corresponding to $\Gamma_{u'}$ for some $u' \in \U$, and hence we contradict $\U$ being minimum, as $\U \setminus \{u\}$ would be a representative set of strictly smaller cardinality.

4 $\Rightarrow$ 3:
We want to show that for each $\theta \in \Theta$, we cannot have $\Theta \setminus \{\theta\}$ be representative.
Observe we have no duplicate elements of $\Theta$.
Fix $\theta := \Gamma_u \in \Theta$.
Since $\Gamma_u$ is full-dimensional, there is some $p \in \inter{\Gamma_u}$ so that $\{u\} = \Gamma(p)$.
Therefore, $\Theta \setminus \{\Gamma_u\}$ is not representative, so $\Theta$ is a finite minimum representative set for $\Gamma$.
